---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# abscorr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The `abscorr` package provides tidy versions of common structures used by the Australian Bureau of Statistics (ABS).

This package is currently **in development** and subject to change. 
The lifecycle badge will be changed to `stable` when structures are stable 
(should be relatively soon).


Current structures stored in `abscorr` are:

- `anzsco`: occupation levels of the Australian and New Zealand Standard Classification of Occupations (ANZSCO), First Edition, Revision 1, 2009. Cat. 1220.0.
- `anzsic`: industry levels of the Australian and New Zealand Standard Industrial Classification (ANZSIC), 2006 (Revision 1.0). Cat. 1292.0.
- `asced_foe`: field of education levels of the Australian Standard Classification of Education (ASCED), 2001. Cat. 1272.0.
- `asced_qual`: qualification levels of the Australian Standard Classification of Education (ASCED), 2001. Cat. 1272.0.

## Installation

You can install the current version of `abscorr` with:

``` r
remotes::install_github("runapp-aus/abscorr")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(abscorr)
library(dplyr, warn.conflicts = FALSE)

glimpse(anzsco)
glimpse(anzsic)
glimpse(asced_foe)
glimpse(asced_qual)
```
