---
title: "Included Data Structures"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Included Data Structures}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Current structures stored in `strayr` are:

-   `anzsco`: occupation levels of the [Australian and New Zealand
    Standard Classification of Occupations (ANZSCO), First Edition,
    Revision 1, 2009. Cat.
    1220.0](https://www.abs.gov.au/AUSSTATS/abs@.nsf/DetailsPage/1220.0First%20Edition,%20Revision%201?OpenDocument).
-   `anzsic`: industry levels of the [Australian and New Zealand
    Standard Industrial Classification (ANZSIC), 2006 (Revision 1.0).
    Cat.
    1292.0](https://www.abs.gov.au/ausstats/abs@.nsf/0/20C5B5A4F46DF95BCA25711F00146D75?opendocument).
-   `asced_foe`: field of education levels of the [Australian Standard
    Classification of Education (ASCED), 2001. Cat.
    1272.0](https://www.abs.gov.au/ausstats/abs@.nsf/mf/1272.0).
-   `asced_qual`: qualification levels of the [Australian Standard
    Classification of Education (ASCED), 2001. Cat.
    1272.0](https://www.abs.gov.au/ausstats/abs@.nsf/mf/1272.0).

The `strayr` package also loads
[`absmapsdata`](https://github.com/wfmackey/absmapsdata), which contains
the following structures *and their geometry* as `sf` objects:

**ASGS Main Structures**

-   `sa12011`: Statistical Area 1 2011
-   `sa12016`: Statistical Area 1 2016
-   `sa22011`: Statistical Area 2 2011
-   `sa22016`: Statistical Area 2 2016
-   `sa32011`: Statistical Area 3 2011
-   `sa32016`: Statistical Area 3 2016
-   `sa42011`: Statistical Area 4 2011
-   `sa42016`: Statistical Area 4 2016
-   `gcc2011`: Greater Capital Cities 2011
-   `gcc2016`: Greater Capital Cities 2016
-   `ra2011`: Remoteness Areas 2011
-   `ra2016`: Remoteness Areas 2016
-   `state2011`: State 2011
-   `state2016`: State 2016

**ASGS Non-ABS Structures**

-   `ced2018`: Commonwealth Electoral Divisions 2018
-   `sed2018`: State Electoral Divisions 2018
-   `lga2016`: Local Government Areas 2016
-   `lga2018`: Local Government Areas 2018
-   `regional_ivi2008`: Regions for the Internet Vacancy Index 2008
-   `postcodes2016`: Postcodes 2016
-   `dz2011`: Census of Population and Housing Destination Zones 2011
-   `dz2016`: Census of Population and Housing Destination Zones 2016

## Using ABS structures

Loading the package will lazily load the structures listed above. Call
them with their name:

```{r actual-load, include=FALSE}
# use this to make sure README runs with current build
# rather than installed version
devtools::load_all()
library(dplyr, warn.conflicts = FALSE)
library(sf)
```

```{r fake-load, eval=FALSE}
library(sf)
library(strayr)
#> Loading required package: absmapsdata
library(dplyr)
```

```{r glimpse}
glimpse(anzsco)
glimpse(anzsic)
glimpse(asced_foe)
glimpse(asced_qual)
glimpse(sa42016)
glimpse(ced2018)
```
