---
title: "StrayR"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{StrayR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



## Under Construction


## Using ABS structures

Loading the package will lazily load a number of structures, a full list is available in the [reference](../reference/index.html)

```{r actual-load, include=FALSE}
# use this to make sure README runs with current build
# rather than installed version
devtools::load_all()
library(dplyr, warn.conflicts = FALSE)
library(ggplot2, warn.conflicts = FALSE)
```

```{r fake-load, eval=FALSE}
library(strayr)
library(dplyr)
library(ggplot2)
```

```{r glimpse}
glimpse(anzsco2009)
glimpse(anzsic2006)
glimpse(anzsic_isic)
glimpse(asced_foe2001)
glimpse(asced_qual2001)
```

Objects stored in the [`absmapsdata`](https://github.com/wfmackey/absmapsdata) package can be accessed with the `read_absmap` function:

```{r}
library(sf) # loaded to handle sf objects
read_absmap("sa42016")
```


## Converting state names and abbreviations

The `clean_state()` function makes it easy to wrangle vectors of State names and abbreviations - which might be in different forms and possibly
misspelled.

Let's start with a character vector that includes some misspelled state names,
some correctly spelled state names, as well as some abbreviations both malformed
and correctly formed.

```{r create-string}
x <- c("western Straya", "w. A ", "new soth wailes", "SA", "tazz", "Victoria",
       "northn territy")

```

To convert this character vector to a vector of abbreviations for State names,
 use `clean_state()`:

```{r state}
clean_state(x)

```

If you want full names for the states rather than abbreviations:

```{r state-fullnames}

clean_state(x, to = "state_name")

```

By default, `clean_state()` uses fuzzy or approximate string matching to match the 
elements in your character vector to state names/abbreviations. If you only want
to permit exact matching, you can disable fuzzy matching. This means you will 
never get false matches, but you will also fail to match misspelled state names 
or malformed abbreviations; you'll get an `NA` if no match can be found.

```{r state-exact}
 clean_state(x, fuzzy_match = FALSE)

```

If your data is in a data frame, `clean_state()` works well within a `dplyr::mutate()` call:

```{r dplyr}

 x_df <- data.frame(state = x, stringsAsFactors = FALSE)

library(dplyr)
 x_df %>% 
   mutate(state_abbr = clean_state(state))
```

The function `clean_state` can also return an 'unofficial' state/territory colour for use in charts. 

```{r colours}

clean_state("Queensland", to = "colour")


```

The palette `palette_state_name_2016` can be used in ggplot2 for the unofficial colours of states. 

```{r palette}
read_absmap("state2016") %>% 
    ggplot() + 
    geom_sf(aes(fill = state_name_2016), colour = NA) +
    scale_fill_manual(values = palette_state_name_2016) +
    theme_void()
    
```




## Australian public holidays
This package includes the `auholidays` dataset from the [Australian Public Holidays Dates Machine Readable Dataset](https://data.gov.au/data/dataset/australian-holidays-machine-readable-dataset) as well as a helper function `is_holiday`:

```{r is_holiday_example}
str(auholidays)


is_holiday('2020-01-01')
is_holiday('2019-05-27', jurisdictions = c('ACT', 'TAS'))

h_df <- data.frame(dates = c('2020-01-01', '2020-01-10'))

h_df %>%
  mutate(IsHoliday = is_holiday(dates))
```



## Parsing income ranges

The `parse_income_range` function provides some tools for extracting numbers from income ranges commonly used in Australian data. For example:

```{r}

parse_income_range("$1-$199 ($1-$10,399)", limit = "lower")
parse_income_range("$1-$199 ($1-$10,399)", limit = "upper")
parse_income_range("$1-$199 ($1-$10,399)", limit = "mid")

parse_income_range("e. $180,001 or more", limit = "upper")
parse_income_range("e. $180,001 or more", limit = "upper", max_income = 300e3)


parse_income_range("Nil income")
parse_income_range("Negative income")
parse_income_range("Negative income", negative_as_zero = FALSE)


tibble(income_range = c("Negative income",
                        "Nil income",
                        "$1,500-$1,749 ($78,000-$90,999)",
                        "$1,750-$1,999 ($91,000-$103,999)",
                        "$2,000-$2,999 ($104,000-$155,999)",
                        "$3,000 or more ($156,000 or more)")) %>% 
  mutate(lower = parse_income_range(income_range),
         mid   = parse_income_range(income_range, limit = "mid"),
         upper = parse_income_range(income_range, limit = "upper"))
  
```
